---
title: "Xbar and R / Xbar and S Charts / X and MR Charts Notebook"
output: html_notebook
---

### Problem 1

### A craft brewer of beer purchases incoming raw material for certain materials which arrives in bags. The first critical characteristic that purchasing is concerned with is that the Bag Weight is in a state of statistical control, so that they can be assured of the stability of the product they are receiving. You have been provided with a data file titled BagWeight.dat, which contains the Bag Weight data for a particular supplier shipping a raw material to one of the craft breweries. Each time a shipment arrives (roughly each week), a random sample of 5 bags is pulled off the pallet and weighed. The file contains the results for 30 consecutive shipments.


```{r}

# Startup Code
require(lolcat)
require(spc)

# Load the data
data <- read.delim("BagWeight.dat", header = TRUE)

View(data)

str(data)
```

```{r}
# Calculate the mean for each week
weekly_means <- aggregate(Bag_Weight ~ Week, data = data, FUN = mean)

# Calculate the overall mean of the weekly means (centerline for the X-bar chart)
centerline_xbar <- mean(weekly_means$Bag_Weight)

# Print the result
cat("Centerline for X-bar chart: ", round(centerline_xbar, 4), "\n")
```

```{r}
# Calculate the range (max - min) for each week
weekly_ranges <- aggregate(Bag_Weight ~ Week, data = data, FUN = function(x) max(x) - min(x))

# Calculate the overall average of the weekly ranges (centerline for the R-chart)
centerline_r <- mean(weekly_ranges$Bag_Weight)

# Print the result
cat("Centerline for R-chart: ", round(centerline_r, 4), "\n")

```

```{r}
# Step 1: Calculate the centerline for the X-bar chart
weekly_means <- aggregate(Bag_Weight ~ Week, data = data, FUN = mean)
centerline_xbar <- mean(weekly_means$Bag_Weight)

# Step 2: Calculate the centerline for the R-chart
weekly_ranges <- aggregate(Bag_Weight ~ Week, data = data, FUN = function(x) max(x) - min(x))
centerline_r <- mean(weekly_ranges$Bag_Weight)

# Step 3: Define the A2 constant for a sample size of 5
A2 <- 0.577

# Step 4: Calculate the UCL and LCL for the X-bar chart
UCL_xbar <- centerline_xbar + A2 * centerline_r
LCL_xbar <- centerline_xbar - A2 * centerline_r

# Print the results
cat("UCL for X-bar chart: ", round(UCL_xbar, 4), "\n")
cat("LCL for X-bar chart: ", round(LCL_xbar, 4), "\n")
```

```{r}
# Step 1: Calculate the centerline for the R-chart (mean of weekly ranges)
weekly_ranges <- aggregate(Bag_Weight ~ Week, data = data, FUN = function(x) max(x) - min(x))
centerline_r <- mean(weekly_ranges$Bag_Weight)

# Step 2: Define the D3 and D4 constants for a sample size of 5
D3 <- 0      # No lower control limit
D4 <- 2.114  # Upper control limit factor

# Step 3: Calculate the UCL and LCL for the R-chart
UCL_r <- D4 * centerline_r
LCL_r <- D3 * centerline_r  # Since D3 is 0, LCL will be NA

# Print the results
cat("UCL for R-chart: ", round(UCL_r, 4), "\n")
cat("LCL for R-chart: NA\n")  # Since LCL doesn't exist, it's NA
```

```{r}
# Step 1: Calculate the centerline for the R-chart (mean of weekly ranges)
weekly_ranges <- aggregate(Bag_Weight ~ Week, data = data, FUN = function(x) max(x) - min(x))
centerline_r <- mean(weekly_ranges$Bag_Weight)

# Step 2: Define the d2 constant for a sample size of 5
d2 <- 2.326

# Step 3: Calculate sigma (process standard deviation)
sigma <- centerline_r / d2

# Print the result
cat("Estimated sigma: ", round(sigma, 4), "\n")
```

### Problem 2

### An electronics manufacturer makes a touchpad unit for industrial controls applications. The touch pad sheet is prone to registration issues during screen process printing if it is off-size (i.e. too far off nominal), so the Sheared to Width characteristic is critical to their manufacturing process. Data generated through time by randomly sampling and measuring 8 individual sheets (so, n=8) from 31 multiple production lots (k=31) through time have been provided to you in a data file titled ShearedSheet.dat.

```{r}
# Load the required libraries
library(lolcat)
library(spc)

# Load the data from the file
data <- read.delim("ShearedSheet.dat", header = TRUE)

str(data)

colnames(data)
```

```{r}
# Calculate the mean Width Deviation for each subgroup
xbar <- aggregate(Width_Deviation ~ Subgroup, data = data, FUN = mean)

# Calculate the centerline for the Xbar chart
centerline <- mean(xbar$Width_Deviation)

# Print the centerline rounded to four decimal places
print(round(centerline, 4))
```

```{r}
# Calculate the range (max - min) for each subgroup
ranges <- aggregate(Width_Deviation ~ Subgroup, data = data, FUN = function(x) max(x) - min(x))

# Calculate the centerline for the dispersion chart (average range)
centerline_dispersion <- mean(ranges$Width_Deviation)

# Print the centerline rounded to four decimal places
print(round(centerline_dispersion, 4))

```

```{r}
# Calculate the mean Width Deviation for each subgroup
xbar <- aggregate(Width_Deviation ~ Subgroup, data = data, FUN = mean)

# Calculate the centerline for the Xbar chart
centerline_xbar <- mean(xbar$Width_Deviation)

# Calculate the range (max - min) for each subgroup
ranges <- aggregate(Width_Deviation ~ Subgroup, data = data, FUN = function(x) max(x) - min(x))

# Calculate the centerline for the dispersion chart (average range)
centerline_dispersion <- mean(ranges$Width_Deviation)

# A2 constant for subgroup size n = 8
A2 <- 0.373

# Calculate UCL and LCL for the Xbar chart
UCL <- centerline_xbar + A2 * centerline_dispersion
LCL <- centerline_xbar - A2 * centerline_dispersion

# Print UCL and LCL rounded to four decimal places
print(paste("UCL:", round(UCL, 4)))
print(paste("LCL:", round(LCL, 4)))
```

```{r}
# Calculate the range (max - min) for each subgroup
ranges <- aggregate(Width_Deviation ~ Subgroup, data = data, FUN = function(x) max(x) - min(x))

# Calculate the centerline for the dispersion chart (average range)
centerline_dispersion <- mean(ranges$Width_Deviation)

# D4 and D3 constants for subgroup size n = 8
D4 <- 1.864
D3 <- 0.136

# Calculate UCL and LCL for the Range chart
UCL_R <- D4 * centerline_dispersion
LCL_R <- D3 * centerline_dispersion

# Print UCL and LCL rounded to four decimal places
print(paste("UCL for Range chart:", round(UCL_R, 4)))

# Check if LCL is valid or should be considered NA
if (LCL_R < 0) {
  LCL_R <- "NA"
}

print(paste("LCL for Range chart:", LCL_R))
```

### Problem 3
# You are the manager of the Heat Treatment department at Metals
# company. You have recently installed a new furnace, and have randomly measured the temperature in the rear zone of the furnace for 25 consecutive hours; which corresponds to two consecutive production lots. The data are in a file labeled Furnace.dat.

```{r}
# Load the required libraries
library(lolcat)
library(spc)

# Load the data from the file
data <- read.delim("Furnace.dat", header = TRUE)

str(data)

colnames(data)


```

```{r}
# Calculate the centerline (mean) for the X chart
centerline <- mean(data$Furnace_Temperature)
round(centerline, 4)

```

```{r}
# Calculate the moving ranges (absolute differences between consecutive temperatures)
moving_ranges <- abs(diff(data$Furnace_Temperature))

# Calculate the centerline (average of the moving ranges)
centerline_moving_range <- mean(moving_ranges)

# Print the centerline, rounded to 4 decimal places
cat("Centerline for Moving Range Chart:", round(centerline_moving_range, 4), "\n")
```

```{r}
# Calculate the centerline for the X-chart (mean of the data)
CL_X <- mean(data$Furnace_Temperature)

# Calculate the moving ranges (absolute differences between consecutive temperatures)
moving_ranges <- abs(diff(data$Furnace_Temperature))

# Calculate the average moving range
average_moving_range <- mean(moving_ranges)

# Calculate the standard error (average moving range divided by d2 for moving range size 2)
d2 <- 1.128
SE <- average_moving_range / d2

# Calculate the upper and lower control limits for the X-chart
UCL_X <- CL_X + 3 * SE
LCL_X <- CL_X - 3 * SE

# Print the UCL and LCL, rounded to 4 decimal places
cat("Upper Control Limit for X-chart:", round(UCL_X, 4), "\n")
cat("Lower Control Limit for X-chart:", round(LCL_X, 4), "\n")
```


```{r}
# Calculate the moving ranges (absolute differences between consecutive temperatures)
moving_ranges <- abs(diff(data$Furnace_Temperature))

# Calculate the average moving range (centerline for the dispersion chart)
average_moving_range <- mean(moving_ranges)

# Constants for subgroup size of 2
D3 <- 0
D4 <- 3.267

# Calculate the upper and lower control limits for the dispersion chart
UCL_dispersion <- D4 * average_moving_range
LCL_dispersion <- ifelse(D3 == 0, NA, D3 * average_moving_range)

# Print the UCL and LCL, rounded to 4 decimal places
cat("Upper Control Limit for Dispersion Chart:", round(UCL_dispersion, 4), "\n")
cat("Lower Control Limit for Dispersion Chart:", LCL_dispersion, "\n")
```

```{r}
# Calculate the moving ranges (absolute differences between consecutive temperatures)
moving_ranges <- abs(diff(data$Furnace_Temperature))

# Calculate the average moving range (centerline for the dispersion chart)
average_moving_range <- mean(moving_ranges)

# d2 constant for subgroup size of 2
d2 <- 1.128

# Estimate sigma
sigma <- average_moving_range / d2

# Print the estimated sigma, rounded to 4 decimal places
cat("Estimate for sigma:", round(sigma, 4), "\n")
```


